### 2014-09-24 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix page numbering and front matter format; other minor edits

\begin{document}

\bibliographystyle{unsrt}
\pagestyle{empty}

@@

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\pagestyle{plain}
\pagenumbering{roman}

@@

\begin{tabbing}
\hspace{1.5in} \= \\
BC \> Battalion Chief \\
DC \> Division Chief \\
E \> Engine \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
IC \> Incident Command \\
LODD \> Line of Duty Death \\
M \> Medic \\
NIOSH \> National Institute for Occupational Safety and Health \\
NIST \> National Institute of Standards and Technology \\
RIC \> Rapid Intervention Crew \\
RS \> Rescue Squad \\
SFPE \> Society of Fire Protection Engineers \\
T \> Tower \\
\end{tabbing}

@@

\chapter*{\centering Abstract}

@@

\chapter{Introduction}
\label{sec:introduction}

@@

While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor. In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure. The following lines define the gypsum material and surface in the FDS input file:

@@

\begin{table}[!ht]
\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
\begin{tabular}{lll}
\toprule
Parameter                                    &  Description                                  &  Discussion                        \\
\midrule
Simulation Time                              &  9~min                                        &  --                                \\
Grid Cell Size                               &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
Ambient Temperature$^*$                      &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
Reaction: Polyurethane~\cite{SFPE:Tewarson}  &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 26,200~kJ/kg             &                                    \\
Reaction: Wood~\cite{SFPE:Tewarson}          &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 16,400~kJ/kg             &                                    \\
Peak HRRs                                    &  Initial couch fire: 5~MW                     &  Section~\ref{sec:fires}           \\
                                             &  Basement flashover fire: 14~MW               &                                    \\
                                             &  Basement balcony fire: 1~MW                  &                                    \\
Material: Gypsum Board~\cite{WAKILI2007}     &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
                                             &  $\rho$: 810~kg/m$^3$                         &                                    \\
                                             &  $c_{\rm p}$: 1.0~\si{kJ/(kg.K)}              &                                    \\
\bottomrule
\end{tabular}
\footnotesize
\\ $^{*}$Initial interior temperature was assumed to be 20~$^{\circ}$C; actual exterior temperature was 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
\normalsize
\label{tab:model_parameters}
\end{table}

>>>>

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\rhead{}
\chead{}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\pagenumbering{gobble}

\bibliographystyle{unsrt}

@@

\begingroup
\hypersetup{urlcolor=black}
This publication is available free of charge from:
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\pagenumbering{roman}
\setcounter{page}{3}

@@

\begin{tabbing}
\hspace{1.5in} \= \\
BC \> Battalion Chief \\
E \> Engine \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
IC \> Incident Command \\
LODD \> Line of Duty Death \\
NIOSH \> National Institute for Occupational Safety and Health \\
NIST \> National Institute of Standards and Technology \\
SFPE \> Society of Fire Protection Engineers \\
\end{tabbing}

@@

\chapter*{\centering Abstract}
\pagenumbering{gobble}

@@

\chapter{Introduction}
\label{sec:introduction}
\pagenumbering{arabic}
\setcounter{page}{1}

@@

While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, specific heat, and thickness) to account for heat transfer and energy storage in the ceiling, walls, and floor. In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure. The following lines define the gypsum material and surface properties in the FDS input file:

@@

\begin{table}[!ht]
\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
\begin{tabular}{lll}
\toprule
Parameter                                    &  Description                                  &  Discussion                        \\
\midrule
Simulation Time                              &  9~min                                        &  --                                \\
Grid Cell Size                               &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
Ambient Temperature$^*$                      &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
Reaction: Polyurethane~\cite{SFPE:Tewarson}  &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 26,200~kJ/kg             &                                    \\
Reaction: Wood~\cite{SFPE:Tewarson}          &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 16,400~kJ/kg             &                                    \\
Peak HRRs                                    &  Initial couch fire: 5~MW                     &  Section~\ref{sec:fires}           \\
                                             &  Basement flashover fire: 14~MW               &                                    \\
                                             &  Basement balcony fire: 1~MW                  &                                    \\
Material: Gypsum Board~\cite{WAKILI2007}     &  Thermal conductivity: 0.28~\si{W/(m.K)}      &  Section~\ref{sec:materials}       \\
                                             &  Density: 810~kg/m$^3$                        &                                    \\
                                             &  Specific heat: 1.0~\si{kJ/(kg.K)}            &                                    \\
                                             &  Thickness: 1.2~\si{cm}                       &                                    \\
\bottomrule
\end{tabular}
\footnotesize
\\ $^{*}$Initial interior temperature was assumed to be 20~$^{\circ}$C; actual exterior temperature was 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
\normalsize
\label{tab:model_parameters}
\end{table}
